\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Fix capitalisation

The 2022 competition setup was identical to the 2021 setup: The most recent
version of \EVOSUITE (1.1.0) was used, which by default uses
DynaMOSA~\cite{dynamosa} as the search algorithm. No new features were added in
this version, but support for Java 9+ was added, several bugs were fixed, and a
major refactoring was applied to improve the code quality with respect to the
use of Java generics internally. While several smaller bugfixes were applied in
the run-up to the 2021 competition, no further optimisation or testing was
applied for 2022.

>>>>

The 2022 competition setup was identical to the 2021 setup: The most recent
version of \EVOSUITE (1.1.0) was used, which by default uses
DynaMOSA~\cite{dynamosa} as the search algorithm. No new features were added in
this version, but support for Java 9+ was added, several bugs were fixed, and a
major refactoring was applied to improve the code quality with respect to the
use of Java Generics internally. While several smaller bugfixes were applied in
the run-up to the 2021 competition, no further optimisation or testing was
applied for 2022.
